### 2019-05-19 README.rmd
updating rclean

- Have you ever written a long script in R that conducts oodles of
  analyses and wished that someone would come along and make it all
  clearer to understand and use?
- Well you’re not alone. 
- A recent survey of over 1500 scientists reported a crisis of
  reproducibility with "selective reporting" being the most cited
  contributing factor and 80% saying code availability is playing a
  role
- We created **Rclean** to help scientists more *easily* write "cleaner" code
- [Rclean](https://github.com/ProvTools/Rclean) provides a simple way
  get the code you need to produce a specific result
- **Rclean** uses data provenance tp capture what your code actually
  does when it’s running and then allows you to pull out the essential
  code that produces specific outputs.
- By focusing in on the specific results you want, **Rclean** let’s
  you spend more energy on your science and less time figuring out
  your code.

@@

You can install the most up to date version easily with
[devtools](https://github.com/hadley/devtools):

```R
install.packages("devtools")
devtools::install_github("ProvTools/cleanR")
```
You will also need to be able to generate data provenance from your
script. This can be done using [provR](https://github.com/ProvTools/):

```R
devtools::install_github("ProvTools/provR")
```

Once installed, per usual R practice, just load the *Rclean* and
*provR* packages:

```R
library(Rclean)
library(provR)
```

@@

Here's a
[demo video](https://asciinema.org/a/osSGbvH3GKA3r3QMJ2Tlba1pu) for
the following example:

[![demo video](Rclean_demo.png)](https://asciinema.org/a/osSGbvH3GKA3r3QMJ2Tlba1pu)

>>>>

- Have you ever written a long script in R that conducts lots of
  analyses and wished that someone would come along and make it all
  clearer to understand and use?
- Well you’re not alone. 
- A recent survey of over 1500 scientists reported a crisis of
  reproducibility with "selective reporting" being the most cited
  contributing factor and 80% saying code availability is playing a
  role.
- [Rclean](https://github.com/ProvTools/Rclean) was created to help
  scientists more *easily* write "cleaner" code by providing a simple,
  rigorous way to isolate the minimal code you need in order to
  produce a specific result (e.g. object, plot, output written to
  disk).
- [Rclean](https://github.com/ProvTools/Rclean) is built on data
  provenance, a formal representation of a computation, and uses graph
  analysis to determine the minimal path from inputs to results.
- The goal is to help facilitate code transparency, reproduciblity,
  reusability and ultimately help scientists spend more time on
  research and less time on software.

@@

You can install the most up to date (beta) version easily with
[devtools](https://github.com/hadley/devtools):

```R
install.packages("devtools")
devtools::install_github("ProvTools/Rclean", ref = "dev")
```

Once installed, per usual R practice, just load the *Rclean*:

```R
library(Rclean)
```

@@

*Rclean* usage is simple. Have a script with code you want to clean
saved to disk.
